import data and set seed
```{r}
hr_data <- read.csv("./HR_Analytics.csv")
set.seed(391)
```

## 1.Which numerical factors significantly influence the monthly income (MonthlyIncome)?

By general understanding, there are some numerical variables that may also have impact on `MonthlyIncome`.
1. Age: Generally, with age comes more work experience, which can often lead to higher salaries. 
2. DailyRate: Higher daily rates could suggest higher overall compensation packages.
3. DistanceFromHome: companies may offer higher salaries to attract talent who have a longer commute.
4. TotalWorkingYears: TotalWorkingYears reflects an employee's experience level. 
5. YearsAtCompany: Long-term employees may have received more incremental salary increases and promotions than newer employees.
So we can do a correlation matrix to these variables
```{r}
cor(hr_data[c("MonthlyIncome", "Age", "DailyRate", "DistanceFromHome", "TotalWorkingYears", "YearsAtCompany")])
```
By the correlation matrix, we can see `TotalWorkingYears` has the most impact on `MonthlyIncome` and `DailyRate` has has less impact on `MonthlyIncome`.

## 2.