library
```{r}
library(tidyverse)
library(lmtest)
library(dplyr)
library(ggplot2)
library(GGally)
library(caret)
library(MASS)
library(car)
```

import data and set seed
```{r}
data <- read.csv("./HR_Analytics.csv")
set.seed(391)
```

preprocess
```{r}
constant_cols <- sapply(dat, function(x) length(unique(x)) == 1)
data <- dat[, !constant_cols]
data <- data[-c(1, 11)]
data$OverTime <- as.integer(factor(data$OverTime)) - 1
data$SalarySlab <- as.integer(factor(data$SalarySlab)) - 1
data$MaritalStatus <- as.integer(factor(data$MaritalStatus)) - 1
data$JobRole <- as.integer(factor(data$JobRole)) - 1
data$Gender <- as.integer(factor(data$Gender)) - 1
data$EducationField <- as.integer(factor(data$EducationField)) - 1
data$Department <- as.integer(factor(data$Department)) - 1
data$BusinessTravel <- as.integer(factor(data$BusinessTravel)) - 1
data$Attrition <- as.integer(factor(data$Attrition)) - 1
data$AgeGroup <- as.integer(factor(data$AgeGroup)) - 1
data$YearsWithCurrManager[is.na(data$YearsWithCurrManager)] <- predict_null
```

## 1. Which numerical factors significantly influence the monthly income (MonthlyIncome)?

By general understanding, there are some numerical variables that may also have impact on `MonthlyIncome`.
1. Age: Generally, with age comes more work experience, which can often lead to higher salaries. 
2. DailyRate: Higher daily rates could suggest higher overall compensation packages.
3. DistanceFromHome: companies may offer higher salaries to attract talent who have a longer commute.
4. TotalWorkingYears: TotalWorkingYears reflects an employee's experience level. 
5. YearsAtCompany: Long-term employees may have received more incremental salary increases and promotions than newer employees.
So we can do a correlation matrix to these variables
```{r}
cor(data[c("MonthlyIncome", "Age", "DailyRate", "DistanceFromHome", "TotalWorkingYears", "YearsAtCompany")])
```
By the correlation matrix, we can see `TotalWorkingYears` has the most impact on `MonthlyIncome` and `DailyRate` has has less impact on `MonthlyIncome`.

## 2. Is it feasible to apply a linear regression model to predict monthly income (MonthlyIncome)?
```{r}
# Full linear regression model
model_full <- lm(MonthlyIncome ~ ., data)
summary(model_full)
```
Explore correlation between each variable
```{r}
# Plot each variable against MonthlyIncome in 2 times 2 matrix
par(mfrow = c(2, 2))

plot(data$JobLevel, data$MonthlyIncome, main = "JobLevel vs MonthlyIncome")
plot(data$TotalWorkingYears, data$MonthlyIncome, main = "TotalWorkingYears vs MonthlyIncome")
plot(data$YearsAtCompany, data$MonthlyIncome, main = "YearsAtCompany vs MonthlyIncome")
plot(data$Age, data$MonthlyIncome, main = "Age vs MonthlyIncome")
plot(data$AgeGroup, data$MonthlyIncome, main = "AgeGroup vs MonthlyIncome")
plot(data$YearsInCurrentRole, data$MonthlyIncome, main = "YearsInCurrentRole vs MonthlyIncome")
plot(data$YearsSinceLastPromotion, data$MonthlyIncome, main = "YearsSinceLastPromotion vs MonthlyIncome")
plot(data$YearsWithCurrManager, data$MonthlyIncome, main = "YearsWithCurrManager vs MonthlyIncome")
plot(data$NumCompaniesWorked, data$MonthlyIncome, main = "NumCompaniesWorked vs MonthlyIncome")
plot(data$Education, data$MonthlyIncome, main = "Education vs MonthlyIncome")
plot(data$Department, data$MonthlyIncome, main = "Department vs MonthlyIncome")
plot(data$MonthlyRate, data$MonthlyIncome, main = "MonthlyRate vs MonthlyIncome")
plot(data$BusinessTravel, data$MonthlyIncome, main = "BusinessTravel vs MonthlyIncome")
plot(data$WorkLifeBalance, data$MonthlyIncome, main = "WorkLifeBalance vs MonthlyIncome")
plot(data$RelationshipSatisfaction, data$MonthlyIncome, main = "RelationshipSatisfaction vs MonthlyIncome")
plot(data$OverTime, data$MonthlyIncome, main = "OverTime vs MonthlyIncome")
plot(data$DailyRate, data$MonthlyIncome, main = "DailyRate vs MonthlyIncome")
plot(data$StockOptionLevel, data$MonthlyIncome, main = "StockOptionLevel vs MonthlyIncome")
plot(data$EnvironmentSatisfaction, data$MonthlyIncome, main = "EnvironmentSatisfaction vs MonthlyIncome")
plot(data$JobSatisfaction, data$MonthlyIncome, main = "JobSatisfaction vs MonthlyIncome")
plot(data$HourlyRate, data$MonthlyIncome, main = "HourlyRate vs MonthlyIncome")
plot(data$PerformanceRating, data$MonthlyIncome, main = "PerformanceRating vs MonthlyIncome")
plot(data$DistanceFromHome, data$MonthlyIncome, main = "DistanceFromHome vs MonthlyIncome")
plot(data$JobInvolvement, data$MonthlyIncome, main = "JobInvolvement vs MonthlyIncome")
plot(data$PercentSalaryHike, data$MonthlyIncome, main = "PercentSalaryHike vs MonthlyIncome")
plot(data$TrainingTimesLastYear, data$MonthlyIncome, main = "TrainingTimesLastYear vs MonthlyIncome")
plot(data$Gender, data$MonthlyIncome, main = "Gender vs MonthlyIncome")
plot(data$EducationField, data$MonthlyIncome, main = "EducationField vs MonthlyIncome")
plot(data$MaritalStatus, data$MonthlyIncome, main = "MaritalStatus vs MonthlyIncome")
plot(data$JobRole, data$MonthlyIncome, main = "JobRole vs MonthlyIncome")
plot(data$Attrition, data$MonthlyIncome, main = "Attrition vs MonthlyIncome")
plot(data$SalarySlab, data$MonthlyIncome, main = "SalarySlab vs MonthlyIncome")
# Create correlation matrix
cor_matrix <- cor(data, use = "complete.obs")
cor_matrix
```

```{r}
# Filter out the uncorrelated predictor based on correlation values and plots.
model_reduced1 <- lm(MonthlyIncome ~ Department + DistanceFromHome + JobLevel + JobRole + SalarySlab + Age + TotalWorkingYears + YearsWithCurrManager, data)
summary(model_reduced1)
```

## 3. Can a more complex model be developed to address multicollinearity issues in predicting monthly income (MonthlyIncome)?
```{r}
# Refine the model using stepwise regression
model_step <- stepAIC(model_full, direction = "both")
summary(model_step)
plot(fitted(model_step), residuals(model_step), main="Residuals vs Predicted Values", xlab="Predicted Values", ylab="Residuals")
abline(h=0, col="red")
```

```{r}
# Check heteroskedasticity
bptest(model_step)
```

```{r}
# Check normality
qqnorm(residuals(model_step))
qqline(residuals(model_step), col = "red")
```

## 4. Between the models considered, which one demonstrates superior predictive performance?

setup 10-fold cross-validation
```{r}
control <- trainControl(method="cv", number=10) 
```

full model
```{r}
model_full_cv <- train(MonthlyIncome ~ .,
                  data=data,
                  method="lm",
                  trControl=control)
model_full_cv
```

reduced model
```{r}
model_reduced_cv <- train(MonthlyIncome ~ Department + DistanceFromHome + JobLevel + JobRole + SalarySlab + Age + TotalWorkingYears + YearsWithCurrManager,
                  data=data,
                  method="lm",
                  trControl=control)
model_reduced_cv
```

stepwise model
```{r}
model_step$call
model_step_cv <- train(MonthlyIncome ~ Age + BusinessTravel + Department + 
    DistanceFromHome + JobLevel + JobRole + SalarySlab + TotalWorkingYears + 
    YearsWithCurrManager,
                  data=data,
                  method="lm",
                  trControl=control)
model_step_cv
```
RMSE: Full model > Reduced model > Stepwise model
Rsquared: Full model < Stepwise model < Reduced model
MAE: Full model > Reduced model > Stepwise model

Overall Performance: Full model < Reduced model < Stepwise model
